---
title: "lab-08 pt.2"
author: "Conor Lacey"
date: '2023-03-05'
output: html_document
---

```{r library}
suppressWarnings(library(tidyverse))
library(skimr)
```


### Introduction

I made a separate markdown document so that I didn't have to wait 3 minutes every time I wanted to load my knitted document.

### Exercise 10

```{r load-data}
uoe_art <- read_csv("data/uoe-art.csv")
```

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, name, year, link)
```

Yes we have some warnings, because some titles don't have a year in parenthesis! As a result, we will have an NA in quite a few rows for the year column.

### Exercise 11

```{r skim}
skim(uoe_art)
```

There are 115 pieces with artist info missing

### Exercise 12

```{r year-plot}
uoe_art %>% ggplot(aes(x = year)) +
  geom_histogram()
```

Strange. There it appears there a piece of art that was created around the time Christ was born. Well, clearly this must be an issue. Let's go take a look. 

### Exercise 13

```{r problem-child}
uoe_art %>% filter(year <  500)
```

When we go to this artwork's page we find that it was actually done in 1964. Let's fix this. 

```{r fixing-Death-Mask}
uoe_art <- uoe_art %>% mutate(year = case_when(year == 2 ~ 1964))
```

### Exercise 14

```{r commonly featured artist}
uoe_art %>% count(name) %>% arrange(desc(n)) %>% head(10)
```

It appears most of their pieces are by Emma Gillies. I have no idea who this is because I'm a quant psych shut-in. It looks like, from a quick Wiki search, that she is famous for her Art Deco style? Sure! If anything this just reflects my knowledge of the art world and how uncultured I am.   

